Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
Lemma formulation
Intro to general model

Now  we discuss the general online
model where the request sequence
can be arbitrary.
In Section~\ref{sec:k3}, we show that the classic \emph{rent-or-buy} approach~\cite{karlin-ski-rental} provides an optimal algorithm for $k=3$.
We showed a lower bound of $\Omega(k \cdot \ell)$ that holds for $k=3$ (cf. Section~\ref{sec:lowerbound}), hence the result from this section is asymptotically optimal.
Furthermore, in Section~\ref{sec:k2}, we show a strictly $6$-competitive algorithm for $k=2$.

@@

\begin{lemma}
	\label{lem:1req}
	In a single reconfiguration of nodes (after a merge of components), \TAlg exchanges at most $2$ pairs of nodes.
\end{lemma}

>>>>

Now  we discuss the general online
model where the request sequence
can be arbitrary.
In Section~\ref{sec:k3}, we show a $O(k \cdot \ell)$-competitive algorithm for $k=3$ using the classic \emph{rent-or-buy} approach~\cite{karlin-ski-rental}.
Prior to this section, we showed a lower bound of $\Omega(k \cdot \ell)$  that holds for the general model, hence the result from this section is asymptotically optimal (cf. Section~\ref{sec:lowerbound}).
Furthermore, in Section~\ref{sec:k2}, we show a strictly $6$-competitive algorithm for $k=2$.

@@

\begin{lemma}
	\label{lem:1req}
	In a single reconfiguration of nodes (after a merge of components), \TAlg exchanges at most two pairs of nodes.
\end{lemma}
